Management induced changes of soil organic carbon on global croplands

### 2020-12-14 SOCbudgetPaper/discussion.Rmd
bugfix mille

The evaluation of SOC stock gains and losses is complex and has several dimensions as climatic and anthropogenic effects overlap. If defining the SOC debt of 1975 as the baseline, and measuring land-use emissions on croplands as the difference between a potential natural state and the state under human interventions (see [@pugh_simulated_2015]), global croplands have acted as a carbon sink since 1975 according to our study. However, annual C sequesteration rates of 0.2 per mille are well below the promoted 4 per mille ([@minasny_soil_2017]), indicating that productivity gains on historic levels alone are not enough to meet ambitious climate targets.

>>>>

The evaluation of SOC stock gains and losses is complex and has several dimensions as climatic and anthropogenic effects overlap. If defining the SOC debt of 1975 as the baseline, and measuring land-use emissions on croplands as the difference between a potential natural state and the state under human interventions (see [@pugh_simulated_2015]), global croplands have acted as a carbon sink since 1975 according to our study. However, annual C sequesteration rates of 0.2 per 1000 are well below the promoted 4 per 1000 ([@minasny_soil_2017]), indicating that productivity gains on historic levels alone are not enough to meet ambitious climate targets.
